% - - - - - - - - - - - -  - - - - - - - - - - - - - - - - - - - - - - - - %
%	References
% - - - - - - - - - - - -  - - - - - - - - - - - - - - - - - - - - - - - - %

\begin{thebibliography}{99}

\bibitem{GDPR2016}
{\sc European Parliament and Council of the European Union}
(2016).
Regulation (EU) 2016/679 on the protection of natural persons with regard to the processing of personal data (General Data Protection Regulation).
\textit{Official Journal of the European Union}, L119, 1--88.
Retrieved March 12, 2026, from \url{https://eur-lex.europa.eu/eli/reg/2016/679/oj}

\bibitem{GitHubFlow}
{\sc GitHub, Inc.}
(2026).
GitHub flow.
Retrieved April 3, 2026, from \url{https://docs.github.com/en/get-started/using-github/github-flow}

\bibitem{ContributingGDPR}
{\sc Guerrero-Toro, C.}
(2026).
\textit{Contributing to gdpr\_anonymizer}.
Retrieved May 7, 2026, from \url{https://github.com/cguerreroto/gdpr_anonymizer/blob/main/CONTRIBUTING.md}

\bibitem{CIGDPR}
{\sc Guerrero-Toro, C.}
(2026).
\textit{Continuous integration workflow for gdpr\_anonymizer}.
Retrieved May 7, 2026, from \url{https://github.com/cguerreroto/gdpr_anonymizer/blob/main/.github/workflows/ci.yml}

\bibitem{TestsGDPR}
{\sc Guerrero-Toro, C.}
(2026).
\textit{Testing guide for gdpr\_anonymizer}.
Retrieved May 9, 2026, from \url{https://github.com/cguerreroto/gdpr_anonymizer/blob/main/tests/README.md}

\bibitem{AstralUV}
{\sc Astral Software Inc.}
(2026).
\textit{uv: Python packaging in Rust}.
Retrieved March 18, 2026, from \url{https://docs.astral.sh/uv/}

\bibitem{UltralyticsTrain}
{\sc Ultralytics}
(2026).
\textit{Train mode documentation}.
Retrieved April 22, 2026, from \url{https://docs.ultralytics.com/modes/train}

\bibitem{PytestCov}
{\sc pytest-cov contributors}
(2026).
\textit{pytest-cov documentation}.
Retrieved May 11, 2026, from \url{https://pytest-cov.readthedocs.io/}

\bibitem{CoveragePy}
{\sc Coverage.py contributors}
(2026).
\textit{Coverage.py documentation}.
Retrieved May 11, 2026, from \url{https://coverage.readthedocs.io/}

\bibitem{UnittestMock}
{\sc Python Software Foundation}
(2026).
\textit{unittest.mock --- mock object library}.
Retrieved May 14, 2026, from \url{https://docs.python.org/3/library/unittest.mock.html}

\bibitem{OpenCV}
{\sc OpenCV team}
(2026).
\textit{OpenCV documentation}.
Retrieved April 30, 2026, from \url{https://docs.opencv.org/}

\bibitem{RustClippy}
{\sc Rust Project Developers}
(2026).
\textit{The clippy book}.
Retrieved March 25, 2026, from \url{https://doc.rust-lang.org/clippy/}

\bibitem{PolyFormNC}
{\sc PolyForm Project}
(2026).
\textit{PolyForm Noncommercial License 1.0.0}.
Retrieved May 5, 2026, from \url{https://polyformproject.org/licenses/noncommercial/1.0.0/}

\end{thebibliography}
